
\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{parskip}  % Adds space between paragraphs
\setlength{\parindent}{0pt} % Remove paragraph indentation
\setlength{\parskip}{0pt} % Reduce space between paragraphs
\setlist[itemize]{itemsep=0pt, topsep=0pt,} % Reduce space in itemize lists
\setlist[itemize,1]{itemsep=0pt, topsep=0pt, parsep=0pt, partopsep=0pt} % Reduce space for the first level
\setlist[itemize,2]{itemsep=0pt, topsep=0pt} % Reduce space for the second level
\usepackage{hyperref}  % For clickable links
\usepackage{fontawesome5}  % For icons

\begin{document}

\begin{center}
    \textbf{\Large Hasnain Habib Sayed} \\

    \vspace{0.2em}
    
    Chattogram, Bangladesh \\

    \vspace{0.2em}
    
    \faPhone\hspace{0.5em}\href{tel:01835491586}{01835-491-586} \\
    
    \vspace{0.2em}
    
    \faEnvelope\hspace{0.5em}\href{mailto:hasnain.habib.sayed@gmail.com}{hasnain.habib.sayed@gmail.com} \\

    \vspace{0.2em}
    
    \begin{minipage}[t]{0.135\textwidth}
        \centering
        \faLinkedin\hspace{0.3em}\href{https://linkedin.com/in/has9sayed}{has9sayed}
    \end{minipage}
    \begin{minipage}[t]{0.135\textwidth}
        \centering
        \faGithub\hspace{0.3em}\href{https://github.com/has9sayed}{has9sayed}
    \end{minipage}

\end{center}



\noindent\rule{\textwidth}{0.5pt}

\section*{\normalsize SUMMARY}
CSE graduate from BRAC University, keen to build a strong foundation in web and software development.

\vspace{0.3em}

Passionate about learning, contributing to open-source projects, and improving my skills in real-world

\vspace{0.3em}

software and web development environments.

\section*{\normalsize EDUCATION}
\begin{itemize}[leftmargin=0.2in, label={}]
    \item \textbf{B.Sc. in Computer Science and Engineering}, BRAC University, Dhaka \hfill \textit{2020 – 2024} \\
    CGPA: 3.36

    \vspace{0.5em}
    
    \item \textbf{Higher Secondary Certificate}, Hazera-Taju University College, Chattogram \hfill \textit{2017 – 2019} \\
    GPA: 4.17

    \vspace{0.5em}
    
    \item \textbf{Secondary School Certificate}, Govt. Muslim High School, Chattogram \hfill \textit{2017} \\
    GPA: 4.95
\end{itemize}

\section*{\normalsize EXPERIENCE}
\begin{itemize}[leftmargin=0.2in, label={}]
    \item \textbf{IT Apprentice}, Robotics Club of BRAC University (ROBU) \hfill \textit{2020 – 2021} \\
    \vspace{-0.8em}    
    \begin{itemize}[leftmargin=0.2in, label={--}, itemsep=0pt, topsep=0pt]
        \item Designed graphics for various club events, including logos, banners, and promotional materials.
    \end{itemize}

    \vspace{1em} % Adjust this value for more or less space

    \item \textbf{Participant}, BRACU Intra University Programming Contest Fall 2022 \hfill \textit{2022} \\
    \vspace{-0.8em}
    
    \begin{itemize}[leftmargin=0.2in, label={--}, itemsep=0pt, topsep=0pt]
        \item Competed in a university-wide programming contest and secured 16th place.
    \end{itemize}
\end{itemize}

\section*{\normalsize PROJECTS}
\begin{itemize}[leftmargin=0.2in, label={}]
    \item \textbf{Co-Developer}, Swappr (Online Platform for Course Swapping) \hfill \textit{2022} \\
    \vspace{-0.8em}
    \begin{itemize}[leftmargin=0.2in, label={--}]
        \item Developed a platform to facilitate course swapping for students.
        \vspace{0.5em}
        \item The platform can be accessed at \href{https://swappr-bracu.web.app}{swappr-bracu.web.app}.
    \end{itemize}
\end{itemize}

\section*{\normalsize INTERESTS}
\begin{itemize}[leftmargin=0in, label={}]
    \item \textbf{Coding Competitions}: Passionate about participating in coding challenges.
    \vspace{0.5em}
    \item \textbf{Video Game Development}: Learning game development and creating small projects on Unity Engine.
    
    \vspace{0.5em}
    
    \item \textbf{Open Source Contributions}: Actively contributing to open source projects.
\end{itemize}

\section*{\normalsize SKILLS}
\begin{itemize}[leftmargin=0.2in, label={}]
    \item \textbf{Programming/Coding}: Python, Java, C++.
    \vspace{0.5em}
    \item \textbf{Frontend Development}: HTML, CSS, JavaScript, React, TypeScript.
    
    \vspace{0.5em}
    
    \item \textbf{Design}: Illustration, logo and banner creation.
\end{itemize}

\section*{\normalsize LANGUAGES}
\begin{itemize}[leftmargin=0.2in, label={}]
    \item \textbf{Bangla}: Native
    \vspace{0.5em}
    \item \textbf{English}: Fluent
\end{itemize}

\end{document}
